\documentclass[tog]{acmsiggraph}
\input{sec/tweaks.tex}
\title{Convolution surfaces model  for hand tracking}
\author{}
\pdfauthor{Secret}

\input{sec/teaser.tex}

\begin{document}
\maketitle

\input{sec/abstract.tex}
\input{sec/intro.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{sec/contributions.tex}

\subsection{Contributions}

\subsubsection*{1. Suggested a hand model representation well suited for user-specific adaption, tracking and animation}

TODO: 

\begin{itemize}
\item Modeling. Implement initialization for the model fitting by running Htrack and putting the hand in a similar pose. 
\item Skinning. Display the texture on the model. For that a parametrization is required. Potentially create ``bumps map'' to apply the errors from model fitting stage. 
\end{itemize}

\subsubsection*{1a. Proposed a single optimization framework for modeling and tracking}

TODO:

\begin{itemize}
\item Run a couple of iteration of ARAP for palm after IK optimization just with data term.
\end{itemize}

\subsubsection*{1b. Developed a tracking model that represents all the degrees of freedom of human hand without creating inexistent degrees. (Not guaranteed by the other approaches, look how model adaptation paper finds the degrees of freedom)}

\subsubsection*{Improved accuracy of state-of-art hand tracking system}

TODO: 

\begin{itemize}
\item Add outline term, time interpolation of initial joint angles, downsampling of the sensor data, fingertips term.
\end{itemize}


\input{sec/related-literature.tex}

%\input{sec/tracking.tex}
%\input{sec/results.tex}
 \input{sec/acks.tex}
\input{sec/biblio.tex}

\appendix
\input{sec/modeling.tex}

\end{document}
